% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Greg H. Martin}
% \address used twice to have two lines of address
\address{650 Mendocino Drive, Ukiah, CA 95482}
\address{GregMartinUCB@gmail.com (707)695-2062}

 
\begin{resume}


 
\section{EDUCATION} {\sl Bachelor of Arts,} Physics
 
                University of California Berkeley, Berkeley, CA,\\ 
                May 2015 \\
         

\section{WORK EXPERIENCE}
{\sl Unity and Fullstack Developer} \hfill June 2016 - July 2016 \\
MyLine\\
934 Howard Street, San Francisco, CA 94103\\
1(310)754-0133\\
Responsibilities:
\begin{itemize} \itemsep -2pt 
\item Make the UI for MyLine's custom men's suit application in Unity3d and develop the API to communicate with the servers.

\item Create, maintain, and improve the backend using django, Amazon's elastic beanstalk, and Amazon's Relational Database Service. 

\item Make and maintain a new landing page for the company. 

\item Integrate Stripe's API for our e-commerce application.
\end{itemize}


{\sl Indie Game Developer} \hfill Winter 2015 - Present \\
Working on a VR exercise game for the HTC Vive using Unity3d and C\#.

 {\sl Undergraduate Research Assistant} \hfill Summer 2014-Summer 2015 \\
                Redwood Center for Theoretical Neuroscience, DeWeese Lab,\\ 
                UC Berkeley, CA\\
            		Responsibilities:
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Editing a currently existing artificial neural-network and implementing new features.
                 \item Collecting, analyzing, and graphing data from the artificial neural-network. 
                 \item Modulation of the code for the neural-network and implementing GPU's to decrease learning time.
                \end{itemize}
                
               {\sl Substitute teacher K-12} \hfill October 2015 - June 2016\\
               Ukiah Unified School District
\section{COMPUTER \\ SKILLS} C\#, Unity3d, Python, Django, Amazon Elastic Beanstalk, Amazon RDS, Amazon EC2, HTML, Blender, Excel, Office, Powerpoint\\
			
                GitHub:  github.com/GregMartinUCB\\
                Website: http://gregmartinucb.github.io\\

	

				               
 
\section{Work Related Skills}
  Attributes that I bring to a team, beyond my computer expertise are my abilities to delegate, to listen to others ideas, to bring a team together, to remain diplomatic and work centered, to be organized, willing to accept constructive criticism, possessing excellent verbal and social skills, as well as willing to take the initiative to look for questions, problems, or simply that next step that needs to be taken to make the product better. All these skills and more I bring to a business to assist it in running smoothly and consistently. 

\end{resume}
\end{document}







